---
title: "Lab6_task"
author: "vicshi94"
date: "2024-02-26"
output: html_document
---

## Task - Works of Shakespeare

Let's start with pre-tokenized data from the works of Shakespeare.

```{r modeling}
# environment setup
suppressMessages(library(text2vec))

load('shakes_words_df_4text2vec.RData')
# Given that the data is pre-tokenized, we can directly create a word embedding model
it = itoken(
  list(shakes_words$word),
  progressbar = FALSE 
)

## Please continue to write the following codes to contrust the final word_vectors
## Simple pipeline
## 1. create_vocabulary
## 2. prune_vocabulary(..., term_count_min = N)
## 3. vocab_vectorizer
## 4. create_tcm
## 5. glove
## 6. got word_vectors
```

**A. Choose a word (e.g., "romeo", "juliet") and then find the 5 words most closely related to your word;**

```{r func_findCloseWords}
## NO NEED TO MODIFY CODES HERE ##
findCloseWords = function(w,dist,n) {
  words = rownames(dist)
  i = which(words==w)
  if (length(i) > 0) {
    res = sort(dist[i,])
    res = as.matrix(res[2:(n+1)])
    colnames(res) = c("distance")
    print(res)
  } 
  else {
    print("Word not in corpus.")
  }
}
dist = dist2(word_vectors, method="cosine")
## NO NEED TO MODIFY CODES HERE ##
```

```{r closest_words}
findCloseWords(
  "word", # <-------------- Change word here, e.g., "romeo", "juliet" 
  dist, 5)
```

**B. Construct a single dimension (e.g., gender, social class) with 1-3 pairs of words, and choose 3-5 words to evaluate their positioning on this axis. Following your analysis, please also briefly summarize your observations.**

```{r func_constructDim}
## NO NEED TO MODIFY CODES HERE ##
norm_vec <- function(x) sqrt(sum(x^2))
dot <- function(x,y) (sum(x*y))
cos <- function(x,y) dot(x,y)/norm_vec(x)/norm_vec(y)
nrm <- function(x) x/norm_vec(x)
dimension <- function(x,y) nrm(nrm(x)-nrm(y))
cdfmn <- function(v) t(apply(as.matrix(data.frame(v)),1,nrm))
make_dim<-function(embedding,pairs,ndim){
  word_dims<-data.frame(matrix(NA,nrow(pairs),ndim))
  for (j in 1:nrow(pairs)){
    rp_word1<-pairs[j,1]
    rp_word2<-pairs[j,2]
    tryCatch(word_dims[j,]<-dimension(embedding[rp_word1,],embedding[rp_word2,]),error=function(e){})
  }
  dim_ave<-colMeans(word_dims, na.rm = TRUE)
  dim_ave_n<-nrm(dim_ave)
  return(dim_ave_n)
}
## NO NEED TO MODIFY CODES HERE ##
```

**========== HINTS ==========**

1.  Directly open "dim_pairs.csv" in Excel, change pair of words and **SAVE**. Content may like this:

| **poor** | **rich** |
|----------|----------|
| ...      | ...      |
| ...      | ...      |

\* You can also explore other dimensions : ) For more examples of pair of words, please refer to the two optional readings (or their supplement materials) in this week.

2.  Continue:

```{r projection}
dim_pairs <- read.csv(
  "dim_pairs.csv", # <---------------- If this is not your csv filename, change it.
  header=FALSE, stringsAsFactor=F
  ) 
construct_dim<-make_dim(
  word_vectors,dim_pairs,
  50 # <--------------------- Your rank number in glove()
  )
dim_proj<-cdfmn(word_vectors)%*%construct_dim

target_words = c("romeo", "juliet") # <------------- Change these words

dim_proj[target_words,]
```

3.  Remember Hand in an RMarkdown file (in HTML/pdf format) with code, output, and your interpretation.
